---
title: Grouped Summary with tapply
author: porter
date: '2018-02-23'
slug: grouped-summary-with-tapply
categories: ['Data Visualization','R']
tags: ['R','DataViz']
description: ['Generating grouped 5-stat summaries with tapply()']
keywords: ['rstats']
---


```{r global_options, include=FALSE}

knitr::opts_chunk$set(
    fig.align = 'center'
    , message = FALSE
    , warning = FALSE
    , error = FALSE
    , cache = TRUE
  )

```

<h1>COPY / PASTE HERE: </h1>

> tapply( d.in$metric, d.in$group, summary)

This is a quick one and sourced from [this](https://stackoverflow.com/questions/9847054/how-to-get-summary-statistics-by-group) SO answer but I kept googling it so wanted to just put it up here.

I'll often want to quickly view 5-stat summaries of a grouped dataframe. `tapply` isn't really a purrr or dplyr approach so people might not think it is elegant but everything I'm googling for purrr or dplyr solutions to this problem statement are really verbose. This is a one-liner.

```{r tapply}

tapply(mtcars$wt, mtcars$cyl, summary)

```

